---
title: "PROSPERO Registrations"
subtitle: "Systematic Review Protocols"
page-layout: article
toc: false
date: last-modified
date-format: "MMMM YYYY"
execute:
    echo: false
    warning: false
    error: false
    freeze: auto
lightbox: true
title-block-categories: true
draft: false
---

```{r setup}
#| include: false
library(gt)
library(tidyverse)

# Read data from Excel file
prospero_data <- read.csv("prospero-registrations.csv") %>%
  mutate(
    year = as.numeric(year),
    highlight = replace_na(highlight, FALSE)
  )
```

## Registered Systematic Reviews

I maintain a commitment to transparency of methods and reporting through prospective registration of systematic review protocols on [PROSPERO](https://www.crd.york.ac.uk/prospero/), the international database of systematic reviews. Below are my registered protocols.

```{r prospero-table}
prospero_data %>%
  arrange(desc(year), desc(registration)) %>%
  mutate(
    # Clean registration display
    registration_clean = registration,
    # Clean title with focus
    title_clean = paste0("**", title, "**"),
    focus_clean = paste0("*", focus, "*"),
    # Status with emojis
    status_clean = case_when(
      status == "Published" ~ "âœ…Published",
      status == "Ongoing" ~ "ðŸ”„Ongoing", 
      status == "Completed" ~ "âœ… Completed",
      TRUE ~ status
    ),
    # Add highlight if needed
    highlight_text = if_else(highlight, " ðŸ†", "")
  ) %>%
  select(registration_clean, title_clean, focus_clean, status_clean, year, url) %>%
  gt() %>%
  cols_label(
    registration_clean = "Registration",
    title_clean = "Title",
    focus_clean = "Focus Area",
    status_clean = "Status", 
    year = "Year",
    url = "Link"
  ) %>%
  fmt_markdown(columns = c(title_clean, focus_clean)) %>%
  fmt_url(columns = url, label = "View") %>%
  cols_align(
    align = "center",
    columns = c(status_clean, year)
  ) %>%
  cols_width(
    registration_clean ~ px(140),
    title_clean ~ px(300),
    focus_clean ~ px(140),
    status_clean ~ px(100),
    year ~ px(60),
    url ~ px(60)
  ) %>%
  tab_options(
    table.font.size = px(13),
    data_row.padding = px(12),
    column_labels.font.weight = "bold",
    column_labels.background.color = "#f8f9fa",
    column_labels.padding = px(8),
    table.border.top.style = "solid",
    table.border.top.width = px(1),
    table.border.top.color = "#dee2e6",
    table.width = pct(100),
    table.margin.left = px(0),
    table.margin.right = px(0)
  ) %>%
  tab_style(
    style = cell_borders(
      sides = "bottom",
      color = "#f1f3f4",
      weight = px(1)
    ),
    locations = cells_body()
  ) %>%
  tab_style(
    style = cell_fill(color = "#fafbfc"),
    locations = cells_body(rows = seq(2, nrow(prospero_data), 2))
  )
```

## Research Areas

::: {.grid}
::: {.g-col-12 .g-col-md-4}
### Cardiovascular Imaging
- Stress CMR protocols
- Diagnostic accuracy studies  
- Prognostic evaluations
:::

::: {.g-col-12 .g-col-md-4}
### Heart Transplantation
- Surveillance strategies
- Safety assessments
- Outcome optimization
:::

::: {.g-col-12 .g-col-md-4}
### Clinical Cardiology
- Valvular disease
- Pericardial conditions
- Interventional guidance
:::
:::

## Methodological Excellence

All protocols adhere to international standards:

- **PRISMA** guidelines for transparent reporting
- **GRADE** methodology for evidence assessment  
- **Cochrane** risk of bias evaluation tools
- **Advanced meta-analysis** using contemporary statistical methods